\mytitle

### 2016-10-30 pdocs/thesis/article.tex
working on Peter's comments
acm tog styling of article started

% Simo.Nikula@gmail.com
% based on latex template at http://www.lut.fi/web/en/library/dissertations1 
\def\mytitle{Description of plasticity in physics engine}
\def\myisbn{978-952-265-XXX-X}
\def\mypdfisbn{978-952-265-XXX-X}
\def\myyear{2017}
\def\mymonth{May}
\def\myname{Simo Nikula}
\def\lut{Lappeenranta University of Technology}
\def\bullet{Bullet Physics}
\def\demolisher{DemolisherDemo}
\def\charpy{CharpyDemo}
\documentclass[a4paper,twoside,12pt,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{lastpage}   % page count
\usepackage{amsmath}
\usepackage{listings}
% \usepackage{mathdots}  % improved \ddots and \iidots
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage[intoc]{nomencl} % including table of content
\usepackage{ifthen}
\usepackage[hmargin=2.0cm,vmargin=1.6cm]{geometry} % setting marginals
\usepackage{fancyhdr,extramarks}  % header ja footer manipulation
\usepackage{times}  % to change font to times
\usepackage{setspace} % for linespacingx
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usepackage{caption}
\usepackage{varwidth}
\usepackage{enumitem} % 
\newcommand{\nomunit}[1]{\renewcommand{\nomentryend}{\hspace*{\fill}#1}} % Inserts units on the right at symbol list
\renewcommand{\nomgroup}[1]{%
 \ifthenelse{\equal{#1}{C}}{\item[\textbf{Latin alphabet}]\item}{%
 \ifthenelse{\equal{#1}{G}}{\item\item[\textbf{Greek alphabet}]\item}{}}{%
 \ifthenelse{\equal{#1}{L}}{\item\item[\textbf{Subscripts}]\item}{}}{%
 \ifthenelse{\equal{#1}{H}}{\item\item[\textbf{Superscripts}]\item}{}}{%
 \ifthenelse{\equal{#1}{W}}{\item\item[\textbf{Abbreviations}]\item}{}}{}}

\singlespacing

\pagestyle{fancy}
\fancyhf{}% clearing the header and footer
\fancyhead[LE,RO]{\bfseries\thepage}    % page number to header
\fancyhead[LO]{\nouppercase{\bfseries\rightmark}}     %
\fancyhead[RE]{\nouppercase{\bfseries\leftmark}}%

\renewcommand\sectionmark[1]
 {\markboth{\thesection\ #1}{}}         % section name to header
\renewcommand\subsectionmark[1]
 {\markright{\thesubsection\ #1}}       % subsection name to header
\renewcommand{\headrulewidth}{0.5pt}    % ruler thickness between head and body
\renewcommand{\footrulewidth}{0pt}      % no ruler between body and footer

\setlength{\nomitemsep}{-\parsep}   % removing default extra skip between entries at nomenclature

\numberwithin{equation}{section}    % equation numbers with section numbers
\numberwithin{table}{section}       % table numbers with section numbers
\numberwithin{figure}{section}      % figure numbers with section numbers

% makeindex command needs to run at command prompt to create nomenclature list file
\makenomenclature % makeindex main_v2.nlo -s nomencl.ist -o main_v2.nls
%\bibpunct{(}{)}{;}{a}{,}{,}%

\begin{document}

\pagestyle{empty}
\title{\mytitle}
\author{Simo Nikula, Aki Mikkola and Timo Björk}
\author{}
\maketitle
\include{article-introduction}
\include{article-section-2}
\include{article-section-3}
\include{article-conclusion}

\fancyhead[LO]{\nouppercase{\bfseries\firstleftxmark}}%
\fancyhead[RE]{\nouppercase{\bfseries\lastrightxmark}}%
\extramarks{}{References}   % this will remove the "References" to be appearing at the header at first page of bibliography
\extramarks{References}{References}
\bibliographystyle{LUTapa}% LUTapa
\bibliography{ref}%

%\cleardoublepage %

>>>>

% Simo.Nikula@gmail.com
\def\mytitle{Elastic-plastic Constraint for Rigid Body Simulation}
\def\lut{Lappeenranta University of Technology}
\def\bullet{Bullet Physics}
\def\demolisher{DemolisherDemo}
\def\charpy{CharpyDemo}
\def\myvolume{VV}
\def\mynumber{N}
\def\myyear{YYYY}
\def\mymonth{Month}
\def\myaan{XXX}
\def\mydoi{XXXXXXX.YYYYYYY}

\documentclass{acmtog}
\acmVolume{\myvolume}
\acmNumber{\mynumber}
\acmYear{\myyear}
\acmMonth{\mymon}
\acmArticleNum{\myaan}  
\acmdoi{10.1145/\mydoi}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
%\usepackage{natbib}
%\usepackage{lastpage}   % page count
%\usepackage{amsmath}
\usepackage{listings}
% \usepackage{mathdots}  % improved \ddots and \iidots
%\usepackage{amssymb}
%\usepackage[english]{babel}
%\usepackage[intoc]{nomencl} % including table of content
%\usepackage{ifthen}
%\usepackage[hmargin=2.0cm,vmargin=1.6cm]{geometry} % setting marginals
%\usepackage{fancyhdr,extramarks}  % header ja footer manipulation
%\usepackage{times}  % to change font to times
%\usepackage{setspace} % for linespacingx
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usepackage{caption}
\usepackage{varwidth}
\usepackage{enumitem} % 
\begin{document}

\title{\mytitle}
markboth{S. Nikula et al.}{\mytitle}

\title{\mytitle}

\author{SIMO NIKULA {\upshape and} AKI MIKKOLA {\upshape and} TIMO BJÖRK
\affil{\lut}}

\category{I.3.7}{Computer Graphics}{Three-Dimensional Graphics and Realism}[Animation]
\category{I.6.3}{Computer Graphics}{Simulation and Modelling}[Applications]

\keywords{Modeling, Animation, Deformation, Elasticity, Plasticity, Dynamics, Simulation}

\acmformat{Nikula, S., Mikkola, A., Björk, T.,  G. V. G. \myyear. 
\mytitle.  {ACM Trans. Graph.} \myvolume, \mynumber, Article \myaan (\mymon \myyear), # pages.\newline  DOI $=$
10.1145/\mydoi\newline http://doi.acm.org/10.1145/\mydoi}

\maketitle

\begin{bottomstuff}

Authors' addresses: Simo.Nikula@gmail.com
\end{bottomstuff}

\include{article-introduction}
\include{article-section-2}
\include{article-section-3}
\include{article-conclusion}

\bibliographystyle{acmtog}
\bibliography{ref}
